\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-24 paper.tex
Appendix D

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(est) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
\multirow{3}{*}{$d\!=\!(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs} \\
\hline
$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived and admitted demands\footnote{When an admitted demand finishes, it will be removed from $\hat{D}$.} }\\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$\hat{D}$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$c_e, c_t$ &\multicolumn{6}{|l}{the remaining capacity on link $e$ or a tunnel $t$}\\
\hline
$\mathbf{z}\in Z$ &\multicolumn{6}{|l}{a network failure scenario in the scenario set}\\
\hline
$p_{\mathbf{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\mathbf{z}$ occurs}\\
\hline
$v_t^{\mathbf{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\mathbf{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

%\subsection {Traffic Engineering for Diverse Availability Targets }\label{BATE}
%Based on the the network scenarios, we design our traffic engineering algorithm that optimizes bandwidth-based availability for diverse services.
%To this end, we introduce the problem formulation of $\mathsf{BATE}$ problem and 
 \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}} 
\KwOut{Whether the new demand can be admitted.}
%$g_d=0, s_d=1, \forall d \in D$; \\
%$f_{d}^t = 0, \forall d \in D ,  k\in K: t\in T_{k}$;\\
\While{$true$}{
$d=\arg_{d'\in D}min\{\sum_{k\in K}b_{d'}^k\times \beta_{d'}\}$;\\
\For{$k\in K$}{
\If{$b_{d}^k >$  remaining capacity of s-d pair $k$}{
    \Return $ False$;\\
}
$T'_k=T_k$;\\
\While{$b_{d}^k>0$}{
$t=\arg_{t\in T'_k}{\min\{c_t*p_t\}}$;\\
 $f_{d}^t=\min$\{$c_t$, $b_{d}^k$\};\\
$ T'_k=T'_k \setminus t$;\\
 $s_d=s_d*p_t$;\\
 $b_{d}^k = b_{d}^k- f_{d}^t;$\\
  $c_t= c_t- f_{d}^t;$\\
}
%\For{$t\in T_k$}{
%   $f_{d}^t=Allocation(t, \mathbf{b}^k_d)$;\\
%   \If{$f_{d}^t>=0$}{
%   $s_i=s_i*p_t$;\\
%   $\mathbf{b}^k_d = \mathbf{b}^k_d- f_{d}^t;$\\
%   }
%   \If{$\mathbf{b}^k_d<=0$}{
%   \textbf{break};\\
%   }
%}
}
  \If{$s_d <   \beta_{d}$}{
      \Return $False$;\\
  }
  $D=D\setminus d$;\\
}

@@

%We now introduce the admission control problem when all the admitted demands can be rescheduled.
%
%We begin with the constraints.
The greedy algorithm tries to conjecture, in an efficient way, whether an allocation strategy satisfying all demands (i.e., including $d$) exists. It works iteratively as follows. In each iteration, 
It finds the demand which has the smallest product of bandwidth target and availability target (i.e., $\sum_{k \in K}\mathbf{b}_d^k \times \beta_d$) at first (line 2), 
and tries to allocate bandwidth for each of its s-d pairs one by one. 
If the remaining network capacity cannot satisfy this demand, we will give up (line 4-5). 
Otherwise, it allocates tunnel bandwidth for this demand, where a tunnel with a smaller product of 
remaining capacity and availability has a higher priority (line 7-13). 
After this, if the availability target cannot be roughly satisfied, we will give up  (line 14-15), 
otherwise, we go for the next iteration.

@@

Finally, our traffic scheduling will minimize the overall bandwith allocated to all admitted demands 
under the above constraints, i.e., 
%thus,  we can finally give the formulation of traffic engineering formulation: 
\begin{equation}
\small
\begin{aligned} \label{BATE-TE}
&minimize \sum_{d \in \hat{D}, k \in K, t \in T_k} f_d^t  \\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t. (\ref{constraint-f2}), (\ref{constraint-e2}), (\ref{Smaller}), (\ref{R2}), (\ref{B2}), (\ref{Achieved})
%\begin{cases}
% \sum_{d \in \hat{D}}\ \sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
\end{array}
\end{aligned}
\end{equation}

@@

Let $A_e^{ \mathbf{z}}$ denote whether link $e$ is available under scenario $ \mathbf{z}$.
The total bandwidth should be smaller than capacity for each available link, i.e.,

@@

\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{d\in \hat{D}}\sum_{k\in K:t\in T^{ \mathbf{z}}_k} f^{t}_{d}u_t^e \le c_e \times A_e^{ \mathbf{z}}
\end{eqnarray}
\end{small}

>>>>

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(est) pair in the set of all s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\hline
\multirow{3}{*}{$d\!=\!(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs} \\
\hline
$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived and admitted demands\footnote{When an admitted demand finishes, it will be removed from $\hat{D}$.} }\\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, \hat{D}$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$\hat{D}$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$\mathbf{b}^k_d$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$c_e, c_t$ &\multicolumn{6}{|l}{the remaining capacity on link $e$ or a tunnel $t$}\\
\hline
$\mathbf{z}\in Z$ &\multicolumn{6}{|l}{a network failure scenario in the scenario set}\\
\hline
$p_{\mathbf{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\mathbf{z}$ occurs}\\
\hline
$v_t^{\mathbf{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\mathbf{z}$}\\
 \hline
  $L_e^{ \mathbf{z}}$ &\multicolumn{6}{|l}{whether link $e$ is available under scenario $ \mathbf{z}$}\\
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

%\subsection {Traffic Engineering for Diverse Availability Targets }\label{BATE}
%Based on the the network scenarios, we design our traffic engineering algorithm that optimizes bandwidth-based availability for diverse services.
%To this end, we introduce the problem formulation of $\mathsf{BATE}$ problem and 
 \begin{algorithm}
\KwIn{Input parameters shown in Table \ref{Notation}} 
\KwOut{Whether the new demand can be admitted.}
%$g_d=0, s_d=1, \forall d \in D$; \\
%$f_{d}^t = 0, \forall d \in D ,  k\in K: t\in T_{k}$;\\
\While{$true$}{
$d=\arg_{d'\in D}min\{\sum_{k\in K}b_{d'}^k\times \beta_{d'}\}$;\\
\For{$k\in K$}{
\If{$b_{d}^k >$  remaining capacity of s-d pair $k$}{
    \Return $ False$;\\
}
$T'_k=T_k$;\\
\While{$b_{d}^k>0$}{
$t=\arg_{t\in T'_k}{\min\{c_t*p_t\}}$;\\
 $f_{d}^t=\min$\{$c_t$, $b_{d}^k$\};\\
$ T'_k=T'_k \setminus t$;\\
 $s_d=s_d*p_t$;\\
 $b_{d}^k = b_{d}^k- f_{d}^t;$\\
  $c_t= c_t- f_{d}^t;$\\
  \textit{Update remaining link capacity} ;\\
}
%\For{$t\in T_k$}{
%   $f_{d}^t=Allocation(t, \mathbf{b}^k_d)$;\\
%   \If{$f_{d}^t>=0$}{
%   $s_i=s_i*p_t$;\\
%   $\mathbf{b}^k_d = \mathbf{b}^k_d- f_{d}^t;$\\
%   }
%   \If{$\mathbf{b}^k_d<=0$}{
%   \textbf{break};\\
%   }
%}
}
  \If{$s_d <   \beta_{d}$}{
      \Return $False$;\\
  }
  $D=D\setminus d$;\\
}

@@

%We now introduce the admission control problem when all the admitted demands can be rescheduled.
%
%We begin with the constraints.
The greedy algorithm tries to conjecture, in an efficient way, whether an allocation strategy satisfying all demands (i.e., including $d$) exists. It works iteratively as follows. In each iteration, 
It finds the demand which has the smallest product of bandwidth target and availability target (i.e., $\sum_{k \in K}\mathbf{b}_d^k \times \beta_d$) at first (line 2), 
and tries to allocate bandwidth for each of its s-d pairs one by one. 
If the remaining network capacity cannot satisfy this demand, we will give up (line 4-5). 
Otherwise, it allocates tunnel bandwidth for this demand, where a tunnel with a smaller product of 
remaining capacity and availability has a higher priority (line 7-14). 
After this, if the availability target cannot be roughly satisfied, we will give up  (line 15-16), 
otherwise, we go for the next iteration.

@@

Finally, our traffic scheduling will minimize the overall bandwith allocated to all admitted demands 
under the above constraints, i.e., 
%thus,  we can finally give the formulation of traffic engineering formulation: 
\begin{equation}
\small
\begin{aligned} \label{BATE-TE}
&minimize \sum_{d \in \hat{D}, k \in K, t \in T_k} f_d^t  \\
&\begin{array}{r@{\quad}r@{}l@{\quad}l}
s.t.  (\ref{Smaller}), (\ref{R2}), (\ref{B2}), (\ref{Achieved}), (\ref{constraint-f2}), (\ref{constraint-e2})
%\begin{cases}
% \sum_{d \in \hat{D}}\ \sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tu_t^e \le c_e, &\text{$\forall e \in E $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
\end{array}
\end{aligned}
\end{equation}

@@

Let $L_e^{ \mathbf{z}}$ denote whether link $e$ is available under scenario $ \mathbf{z}$.
The total bandwidth should be smaller than capacity for each available link, i.e.,

@@

\begin{small}
\begin{eqnarray} \label{B-constraint}
\sum_{d\in \hat{D}}\sum_{k\in K:t\in T^{ \mathbf{z}}_k} f^{t}_{d}u_t^e \le c_e \times L_e^{ \mathbf{z}}
\end{eqnarray}
\end{small}
